---
title: "A5_revision"
output: html_document
date: "2024-10-28"
---

# run A4 first to set up the env

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(chron)
```

```{r GGIR}
library(GGIR)
# GGIR(datadir="~/Desktop/BayesM10/Ni thesis/test",
#  outputdir="~/Desktop/BayesM10/Ni thesis/test_out",
#  dataFormat = "actiwatch_csv",
#  extEpochData_timeformat = "%Y/%m/%d %H:%M:%S:%f",
#    windowsizes = c(5, 900, 3600),
#    threshold.in = round(100 * (5/60), digits = 2),
#    threshold.mod = round(2500 * (5/60), digits = 2),
#    threshold.vig = round(10000 * (5/60), digits = 2),
#    do.neishabouricounts = TRUE,
#    acc.metric = "NeishabouriCount_x")

# read.myacc.csv("~/Desktop/BayesM10/Ni thesis/test/OL0002_1.csv",
#                rmc.skip = 100,
#                rmc.nrow = Inf,
#                rmc.firstrow.acc = 101,
#                rmc.col.acc = 2:4,
#                rmc.col.temp = 7,
#                rmc.col.time=1,
#                rmc.unit.acc = "g",
#                rmc.unit.temp = "C",
#                rmc.unit.time = "POSIX",
#                rmc.format.time = "%Y-%m-%d %H:%M:%S:%f",
#                rmc.desiredtz = "Europe/London",
#                rmc.sf = 100)

tmpdf<-read.csv("~/Desktop/BayesM10/Ni thesis/test/OL0002_1.csv",skip=100,
                header = F)

names(tmpdf)[1] <- "time"
names(tmpdf)[2:4] <- c("acc.x","acc.y","acc.z")
names(tmpdf)[5] <- "Lux"
names(tmpdf)[7] <- "temperature"
names(tmpdf)[8] <- "SVMgs"

tmpdf$Date <- as.Date(tmpdf$time, format = "%Y-%m-%d")

tmpdf %>% filter(Date == "2015-09-08")
```

```{r}
subjects<-unique(df_hlm$ID)
subjects
```


```{r}
date_info <- read.csv("../../data/movement_data.csv") %>% 
  mutate(Datemdy = as.Date(Date, format = "%m/%d/%y"))
  
df_isiv_day <- readxl::read_xlsx("~/Desktop/BayesM10/Ni\ thesis/summary_data/IS_IV/OL0209_OL0416_daysummary_weekly.xlsx") %>% 
  rbind(readxl::read_xlsx("~/Desktop/BayesM10/Ni\ thesis/summary_data/IS_IV/OL0002_OL0209_daysummary_weekly.xlsx"))

unique(toupper(substr(df_isiv_day$id,1,6)))

df_isiv_actigraph <- read.csv("~/Desktop/BayesM10/Ni\ thesis/summary_data/IS_IV/OL0002-OL0209_ISIV_summary.csv") %>% 
  rbind(read.csv("~/Desktop/BayesM10/Ni\ thesis/summary_data/IS_IV/OL0209-OL0416_ISIV_summary.csv")) %>% 
  mutate(ID = ifelse(grepl("ol08719jun",ID),"ol008719jun",ID))

df_isiv_actigraph$actigraphID <- df_isiv_actigraph$ID
df_isiv_actigraph$ID <- toupper(substr(df_isiv_actigraph$ID,1,6))

df_isiv_actigraph <- df_isiv_actigraph %>% 
  group_by(ID) %>% 
  mutate(actigraphNO = row_number()) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(start_time_ymd = as.Date(strsplit(start_time,"T")[[1]][1]))%>% 
  relocate(actigraphNO,actigraphID,start_time_ymd) %>% 
  left_join(date_info %>% 
              rename(start_time_ymd = Datemdy), by = c("ID","start_time_ymd")) %>% 
  relocate(start_time_ymd,Day,.after = ID)

unique(df_isiv_actigraph$ID)

df_isiv_actigraph<-df_isiv_actigraph %>% 
  group_by(ID) %>% 
  mutate(day_diff = as.numeric(lead(start_time_ymd,1) - start_time_ymd)) %>% 
  mutate(startday = ifelse(is.na(Day),lead(Day,1)-day_diff,Day)) %>% 
  relocate(startday)

df_isiv_actigraph <- left_join(df_isiv_actigraph %>% select(-Allocation),
                               df_demo %>% select(ID,Allocation),
                               by = "ID") %>% 
  relocate(Allocation)
df_isiv_actigraph$Allocation


df_isiv_actigraph_ttest1 <- df_isiv_actigraph %>% 
  group_by(ID,Allocation) %>% 
  summarise(IS_interdailystability = mean(IS_interdailystability),
            IV_intradailyvariability = mean(IV_intradailyvariability))

summary(l1<-lm(IS_interdailystability~Allocation,df_isiv_actigraph_ttest1))
plot_model(l1, type = "pred", terms = "Allocation")

summary(lm(IV_intradailyvariability~Allocation,df_isiv_actigraph_ttest1))

df_isiv_actigraph_ttest2 <- df_isiv_actigraph %>% filter(startday > 0) %>% 
  group_by(ID,Allocation) %>% 
  summarise(IS_interdailystability = mean(IS_interdailystability),
            IV_intradailyvariability = mean(IV_intradailyvariability))

unique(df_isiv_actigraph_ttest$ID)

summary(lm(IS_interdailystability~Allocation,df_isiv_actigraph_ttest2))
summary(lm(IV_intradailyvariability~Allocation,df_isiv_actigraph_ttest2))
```

# combine raw data 
```{r}
file_dir <- '/Users/yanyan/Desktop/BayesM10/Ni\ thesis/raw_data/raw\ data\ per\ min/'
temp.df.master = NULL

for (s in subjects){
  numid = strsplit(s,"L")[[1]][2]
  files <- list.files(file_dir,pattern = numid)
  if (length(files) != 0){
      temp.df.all <- NULL
     for (i in 1:length(files)){
        temp.df <- read.csv(paste0(file_dir,files[i])) %>% select(Date,Time,Lux,Temp,SVMgs) %>% 
        mutate(Datemdy = ifelse(grepl("-",Date), as.Date(Date, format = "%Y-%m-%d"),
                                as.Date(Date, format = "%d/%m/%Y"))) %>% 
        mutate(Datemdy = as.Date(Datemdy))
        temp.df.all <- rbind(temp.df.all,temp.df)
     }

    temp.df.all <- merge(temp.df.all %>%
                           select(-Date),
                         date_info %>%
                           filter(ID == s))

    write.csv(temp.df.all,paste0('../../data/raw_per_minute_data/',s,'.csv'))
  } else {
    print(paste0("no subject", s))
  }
  
  temp.df.master <- rbind(temp.df.master,temp.df.all)
}

write.csv(temp.df.master,paste0('../../data/raw_per_minute_data/per_min_data_master.csv'))
```

# check one subject's data to show that calculated SVG actually makes sense
```{r}
unique(temp.df.all$Day)
temp.df.all$Time_hhmmss <- times(paste0(temp.df.all$Time, ":00"))
temp.df.all$Time_hh <- hours(temp.df.all$Time_hhmmss)

act<-temp.df.all %>%
  mutate(rollmean10h = zoo::rollmean(SVMgs, k = 10*60, na.pad = T, align = "right"),
         rollmean5h = zoo::rollmean(SVMgs, k = 5*60, na.pad = T, align = "right")) %>% 
  group_by(Day) %>%
  summarise(M10_calc = max(rollmean10h, na.rm = T),
            L5_calc = min(rollmean5h, na.rm = T))

act_compare <- date_info %>% 
  filter(ID == s)

ggplot(temp.df.all %>% filter(Day == -7), aes(x = Time_hhmmss, y = SVMgs, color = Time_hh))+
  geom_line()+
  scale_x_continuous(breaks = seq(0,1,0.25), labels = seq(0,1,0.25)*24)+
ggplot(temp.df.all %>% filter(Day == -6), aes(x = Time_hhmmss, y = SVMgs, color = Time_hh))+
  geom_line()+
  scale_x_continuous(breaks = seq(0,1,0.25), labels = seq(0,1,0.25)*24)+
plot_layout(nrow = 2)

df_compare <- merge(act %>% select(Day,M10_calc,L5_calc),
                    act_compare %>% select(Day,M10,L5))

ggplot(df_compare, aes(x = M10_calc, y = M10))+
  geom_point()+
  geom_smooth(method = "lm")+
ggplot(df_compare, aes(x = L5_calc, y = L5))+
  geom_point()+
   geom_smooth(method = "lm")

temp.df.all %>%
  group_by(Day) %>%
  summarise(mean_enmo = mean(SVMgs, na.rm = T))

a<-c(24.17651435,
27.81781778,
22.79077242,
27.85237056,
29.44504234,
22.43111781,
51.3727829,
24.55924973,
9.794146954,
13.43260425,
25.7152424,
24.39114854,
13.37010474,
19.10628107,
30.24616453,
25.49364529,
14.65088236) #copied from OL0209_OL0416_daysummary_weekly.xlsx

b<-temp.df.all %>%
  group_by(Day,Date) %>%
  summarise(mean_enmo = mean(SVMgs, na.rm = T)) %>% 
  ungroup() %>% 
  slice(1:17)

c=cbind(a,b)

ggplot(c, aes(x = a, y = mean_enmo))+
  geom_point()+
  geom_smooth(method = "lm")+
  xlim(0,150)+
  ylim(0,150)+
  geom_segment(x = 0, y = 0, xend = 150, yend = 150, linetype = "dashed")

summary(lm(mean_enmo~a,c))
lm.beta::lm.beta(lm(mean_enmo~a,c))

# seems to be highly correlated. I will use this then.
```
## the conclusion is, yes, we could use the calculated mean as a proxy for the actual mean SVG

## calculate M10, M9 etc. and plot their estimation & correlation
```{r}
find.corr <- function(df,a,b){
  #df is the dataframe
  #a(IV) and b(DV) are the column index to which the model is fitted
  iv <- names(df)[a]
  dv <- names(df)[b]
  my.formula = as.formula(paste0("scale(",iv,") ~ scale(",dv,") + (1|ID)"))
  my.lme <- summary(lmer(my.formula,df))
  return(c(my.lme$coefficients[2,1],my.lme$coefficients[2,5])) #beta, p
}
```

```{r}
activity<-temp.df.master %>%
  group_by(ID) %>% 
  mutate(m10 = zoo::rollmean(SVMgs, k = 10*60, na.pad = T, align = "right"),
         m9 = zoo::rollmean(SVMgs, k = 9*60, na.pad = T, align = "right"),
         m8 = zoo::rollmean(SVMgs, k = 8*60, na.pad = T, align = "right"),
         m7 = zoo::rollmean(SVMgs, k = 7*60, na.pad = T, align = "right"),
         m6 = zoo::rollmean(SVMgs, k = 6*60, na.pad = T, align = "right"),
         m5 = zoo::rollmean(SVMgs, k = 5*60, na.pad = T, align = "right"),
         m4 = zoo::rollmean(SVMgs, k = 4*60, na.pad = T, align = "right"),
         m3 = zoo::rollmean(SVMgs, k = 3*60, na.pad = T, align = "right"),
         m2 = zoo::rollmean(SVMgs, k = 2*60, na.pad = T, align = "right"),
         m1 = zoo::rollmean(SVMgs, k = 1*60, na.pad = T, align = "right")) %>% 
  group_by(ID,Day) %>%
  summarise_at(vars(M10,m10:m1),~max(.x,na.rm = T)) %>% 
  filter(m10 != -Inf,M10 != -Inf)

num.row2 = ncol(activity)-3

my.corr.mat2 <- matrix(nrow = num.row2, ncol = num.row2)
my.corr.pmat2 <- matrix(nrow = num.row2, ncol = num.row2)

rownames(my.corr.mat2) <- names(activity)[4:(num.row2+3)]
colnames(my.corr.mat2) <- names(activity)[4:(num.row2+3)]
rownames(my.corr.pmat2) <- names(activity)[4:(num.row2+3)]
colnames(my.corr.pmat2) <- names(activity)[4:(num.row2+3)]

for (i in 1:num.row2){
  my.corr.mat2[i,i] = 1
  my.corr.pmat2[i,i] = 0
}

for (a in 4:(num.row2+3)){
  for (b in 4:(num.row2+3)){
    if (a != b){
      temp_out <- find.corr(activity,a,b)
      my.corr.mat2[a-3,b-3] = temp_out[1]
      my.corr.pmat2[a-3,b-3] = temp_out[2]
    }
  }
}

ggcorrplot::ggcorrplot(
  my.corr.mat2,
  type = "lower",
  outline.color = "white",
           lab = TRUE)+
  scale_fill_gradientn(limits = c(0.8, 1),
                       colors = c("orange", "white", "steelblue4"),
                       values = scales::rescale(c(0.8, 1.0, 1)))+
  theme(legend.position = "none")

ggsave("../figs/R1_corr_plot.png",width = 5 ,height=4,dpi = 300)

which.hour <- temp.df.master %>%
  group_by(ID,Day) %>% 
  mutate(m10 = zoo::rollmean(SVMgs, k = 10*60, na.pad = T, align = "right"),
         m10_start_time = lag(Time_hh,10*60),
         m10_end_time = Time_hh,
         m10_dur = ifelse(m10_end_time >= m10_start_time,
                          m10_end_time - m10_start_time,
                          m10_end_time + 24 - m10_start_time),
         m10_dur = times(m10_dur))

ggdensity(which.hour$m10_dur)
  # group_by(ID,Day) %>%
  # mutate(max_m10 = max(m10,na.rm = T)) %>% 
  # filter(m10 == max_m10)
```


# IS IV for each week
```{r}
temp.df.master$Time_hhmmss <- times(paste0(temp.df.master$Time, ":00"))
temp.df.master$Time_hh <- hours(temp.df.master$Time_hhmmss)

per_hour_data <- temp.df.master%>%
  # filter(Time_hh > 8 & Time_hh <= 18) %>% 
  group_by(ID,Allocation,Day,Date,Time_hh) %>%
  summarise(mean_enmo = mean(SVMgs, na.rm = T)) %>% 
  ungroup()%>%filter(Day >= -14 & Day <= 28) %>% 
  left_join(df_hlm %>% 
              rename(Day = day) %>% 
              select(ID,Day,Gender,Age,posLog,pos_vmu,movement_L5_mean:time_M10_mu))

per_hour_data$phase[per_hour_data$Day < 1] <- "pre"
per_hour_data$phase[per_hour_data$Day >= 1 & per_hour_data$Day <= 7] <- "post1"
per_hour_data$phase[per_hour_data$Day >= 8 & per_hour_data$Day <= 14] <- "post2"
per_hour_data$phase[per_hour_data$Day >= 15 & per_hour_data$Day <= 21] <- "post3"
per_hour_data$phase[per_hour_data$Day >= 22 & per_hour_data$Day <= 28] <- "post4"

per_hour_data$phase <- factor(per_hour_data$phase, levels = c("pre","post1","post2","post3","post4")) #,"post5","post6"

per_hour_data <- per_hour_data %>%
  mutate(DateTime = as.POSIXct(paste(Date, Time_hh), format = "%m/%d/%y %H"))

# Define a function to calculate IS and IV
calculate_IS_IV <- function(data) {
  n <- nrow(data)
  x_bar <- mean(data$mean_enmo, na.rm = TRUE)
  
  # Interdaily Stability (IS): Correlation of hourly values with their mean values for each hour of the day
  mean_by_hour <- data %>% 
    group_by(Time_hh) %>%
    summarise(mean_hourly_enmo = mean(mean_enmo, na.rm = TRUE))
  
  merged_data <- data %>% 
    left_join(mean_by_hour, by = "Time_hh")
  
  #IS <- cor(merged_data$mean_enmo, merged_data$mean_hourly_enmo, use = "complete.obs")^2
   IS <- (n * sum((merged_data$mean_hourly_enmo - x_bar)^2))/((n-1) * sum((merged_data$mean_enmo - x_bar)^2))
  
  # Intradaily Variability (IV): Measures hour-to-hour variability
  sum_diff_squared <- sum((diff(data$mean_enmo))^2, na.rm = TRUE)
  sum_deviation_squared <- sum((data$mean_enmo - x_bar)^2, na.rm = TRUE)
  IV <- (n * sum_diff_squared) / ((n - 1) * sum_deviation_squared)
  
  return(data.frame(IS = IS, IV = IV))
}

# Apply this function by 'ID' and 'phase'
ISIV_results <- per_hour_data %>%
  group_by(ID, phase,Allocation,Age,Gender) %>%
  arrange(DateTime) %>%
  summarise(IS_IV = list(calculate_IS_IV(cur_data()))) %>%
  unnest_wider(IS_IV) %>% 
  left_join(per_hour_data %>%
              ungroup()%>%
              select(-Gender) %>% 
              group_by(ID, phase,Allocation) %>% 
              summarise_at(vars(mean_enmo:time_M10_mu),~mean(.x,na.rm = T)))

ISIV_results$Allocation[ISIV_results$Allocation == "A"] <- "control"
ISIV_results$Allocation[ISIV_results$Allocation == "B"] <- "lithium"
```

#correlation heatmap
```{r}
find.corr <- function(df,a,b){
  #df is the dataframe
  #a(IV) and b(DV) are the column index to which the model is fitted
  iv <- names(df)[a]
  dv <- names(df)[b]
  my.formula = as.formula(paste0("scale(",iv,") ~ scale(",dv,") + (1 |ID/Allocation)"))
  my.lme <- summary(lmer(my.formula,df))
  return(c(my.lme$coefficients[2,1],my.lme$coefficients[2,5])) #beta, p
}
```

```{r}
num.row2 = ncol(ISIV_results)-6

my.corr.mat2 <- matrix(nrow = num.row2, ncol = num.row2)
my.corr.pmat2 <- matrix(nrow = num.row2, ncol = num.row2)

rownames(my.corr.mat2) <- names(ISIV_results)[6:(num.row2+5)]
colnames(my.corr.mat2) <- names(ISIV_results)[6:(num.row2+5)]
rownames(my.corr.pmat2) <- names(ISIV_results)[6:(num.row2+5)]
colnames(my.corr.pmat2) <- names(ISIV_results)[6:(num.row2+5)]

for (i in 1:num.row2){
  my.corr.mat2[i,i] = 1
  my.corr.pmat2[i,i] = 0
}

for (a in 6:(num.row2+5)){
  for (b in 6:(num.row2+5)){
    if (a != b){
      temp_out <- find.corr(ISIV_results,a,b)
      my.corr.mat2[a-5,b-5] = temp_out[1]
      my.corr.pmat2[a-5,b-5] = temp_out[2]
    }
  }
}

ggcorrplot::ggcorrplot(my.corr.mat2,p.mat = my.corr.pmat2,insig = "blank",colors=c("orange", "white", "steelblue4"),lab = TRUE, digits = 1)

# summary(lmer(movement_M10_mean ~ phase * Allocation + (1|ID),ISIV_results))
```

```{r}

summary(l1<-lmer(IS ~ Allocation * phase + posLog + pos_vmu +Age + Gender+ (1|ID),ISIV_results))
summary(lmer(IS ~ Allocation * phase + posLog + pos_vmu +Age + Gender+ (1|ID),ISIV_results %>% 
               mutate(Allocation = factor(Allocation, levels = c("lithium","control")))))
summary(lmer(IS ~ Allocation * phase + movement_M10_vmu + posLog + pos_vmu +Age + Gender+ (1|ID),ISIV_results))
summary(lmer(IS ~ Allocation * phase + movement_M10_s + posLog + pos_vmu +Age + Gender+ (1|ID),ISIV_results))

ee1 <- as.data.frame(Effect(c("phase", "Allocation"),l1))

stat.test <- as.data.frame(round(summary(l1)$coefficients,3))[11:14,]%>%
  rename(p_val = `Pr(>|t|)`)

stat.test$group1 <- c("post1","post2","post3","post4")
stat.test$group2 <- c("post1","post2","post3","post4")

stat.test <- left_join(stat.test,ee1[ee1$phase != "pre" & ee1$Allocation == "control",]%>%
  rename(group1 = phase))%>%
  mutate(y.position = ee1$upper[1])%>%
  mutate(p_sig = if_else(p_val < 0.001,"***", if_else(p_val < 0.01, "**", if_else(p_val < 0.05, "*", "ns")) ))

p1<-ggplot(ee1, aes(x = phase, y = fit, color = Allocation))+
  scale_color_manual(values=orangeNavyPalette)+
  geom_errorbar(aes(ymin = lower,ymax=upper),width=0.1,color = "black")+
    geom_point(size = 3)+
  geom_line(aes(group = Allocation), linewidth = 1)+
  theme(panel.grid.major.y = element_line(color = "black",size = 0.2),
        panel.grid.minor.y = element_blank(),
         panel.grid.major.x = element_blank(),
        axis.text.x = element_text(angle=45))+
  labs(title = "IS",y="interdaily stability")+ 
  stat_pvalue_manual(stat.test, label = "p_sig",vjust = -1)+
  scale_x_discrete(labels = c("run-in","week 1","week 2","week 3","week 4"))+
  ylim(0.2,0.8)

summary(l2<-lmer(IV ~ Allocation * phase + posLog + pos_vmu +Age + Gender+ (1|ID),ISIV_results))

ee2 <- as.data.frame(Effect(c("phase", "Allocation"),l2))

stat.test <- as.data.frame(round(summary(l2)$coefficients,3))[11:14,]%>%
  rename(p_val = `Pr(>|t|)`)

stat.test$group1 <- c("post1","post2","post3","post4")
stat.test$group2 <- c("post1","post2","post3","post4")

stat.test <- left_join(stat.test,ee2[ee2$phase != "pre" & ee2$Allocation == "control",]%>%
  rename(group1 = phase))%>%
  mutate(y.position = ee2$upper[1])%>%
  mutate(p_sig = if_else(p_val < 0.001,"***", if_else(p_val < 0.01, "**", if_else(p_val < 0.05, "*", "ns")) ))

p2<-ggplot(ee2, aes(x = phase, y = fit, color = Allocation))+
  scale_color_manual(values=orangeNavyPalette)+
  geom_errorbar(aes(ymin = lower,ymax=upper),width=0.1,color = "black")+
    geom_point(size = 3)+
  geom_line(aes(group = Allocation), linewidth = 1)+
  theme(panel.grid.major.y = element_line(color = "black",size = 0.2),
        panel.grid.minor.y = element_blank(),
         panel.grid.major.x = element_blank(),
        axis.text.x = element_text(angle=45))+
  labs(title = "IV",y="intradaily variability")+ 
  stat_pvalue_manual(stat.test, label = "p_sig",vjust = -3)+
  scale_x_discrete(labels = c("run-in","week 1","week 2","week 3","week 4"))+
  ylim(0.4,1.4)

p1+p2+
  plot_annotation(tag_levels = c("a"))
ggsave("../figs/ISIV.png",width = 7 ,height=3,dpi = 300)

```

### vmu and IS

```{r}
summary(lmer(scale(IS) ~ scale(movement_M10_vmu) + (1|ID/Allocation),ISIV_results))

df_change <- ISIV_results %>% 
  group_by(ID, Allocation, phase,Age,Gender) %>% 
  summarise_at(vars(movement_M10_vmu,movement_M10_mean,
                    time_M10_vmu,time_M10_mean,posLog,pos_vmu,IS,IV), ~mean(.x, na.rm = T)) %>% 
  pivot_wider(names_from = phase, values_from = c(movement_M10_vmu,movement_M10_mean,
                                                  time_M10_vmu,time_M10_mean,posLog,pos_vmu,IS,IV)) %>% 
  rowwise() %>% 
  mutate(M10_change = `movement_M10_mean_post4` - `movement_M10_mean_pre`,
         M10_vmu_change = `movement_M10_vmu_post4` - `movement_M10_vmu_pre`,
         timeM10_change = `time_M10_mean_post4` - `time_M10_mean_pre`,
         timeM10_vmu_change = `time_M10_vmu_post4` - `time_M10_vmu_pre`,
         posLog_change = `posLog_post4` - `posLog_pre`,
         pos_vmu_change = `pos_vmu_post4` - `pos_vmu_pre`,
         IS_change = `IS_post4` - `IS_pre`,
         IV_change = `IV_post4` - `IV_pre`)

summary(l1 <- lm(IS_change ~ M10_vmu_change + Age + Gender, df_change))
lm.beta::lm.beta(l1)
ggplot(df_change, aes(y = IS_change, x = M10_vmu_change))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = 0, linetype = "dashed")+
  geom_smooth(method = "lm", color = "black")+
  geom_point(aes(color = Allocation))+
  scale_color_manual(values = orangeNavyPalette)+
  labs(x = "change in M10 volatility",
       y = "change in IS")

summary(l1 <- lm(IV_change ~ M10_vmu_change + Age + Gender, df_change))
ggplot(df_change, aes(y = IV_change, x = M10_vmu_change))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = 0, linetype = "dashed")+
  geom_smooth(method = "lm", color = "black")+
  geom_point(aes(color = Allocation))+
  scale_color_manual(values = orangeNavyPalette)+
  labs(x = "change in M10 volatility",
       y = "change in IV")
```



# IS IV for pre/post
```{r}
per_hour_data <- temp.df.master%>%
  # filter(Time_hh > 8 & Time_hh <= 18) %>% 
  group_by(ID,Allocation,Day,Date,Time_hh) %>%
  summarise(mean_enmo = mean(SVMgs, na.rm = T)) %>% 
  ungroup()%>%filter(Day >= -14 & Day <= 28) %>% 
  left_join(df_hlm %>% 
              rename(Day = day) %>% 
              select(ID,Day,posLog,pos_vmu,movement_L5_mean:time_M10_mu))

per_hour_data$phase[per_hour_data$Day < 1] <- "pre"
per_hour_data$phase[per_hour_data$Day >= 1 & per_hour_data$Day <= 28] <- "post"

per_hour_data$phase <- factor(per_hour_data$phase, levels = c("pre","post")) #,"post5","post6"

per_hour_data <- per_hour_data %>%
  mutate(DateTime = as.POSIXct(paste(Date, Time_hh), format = "%m/%d/%y %H"))


n <- nrow(per_hour_data)
  
# Define a function to calculate IS and IV
calculate_IS_IV <- function(data) {
  n <- nrow(data)
  x_bar <- mean(data$mean_enmo, na.rm = TRUE)
  
  # Interdaily Stability (IS): Correlation of hourly values with their mean values for each hour of the day
  mean_by_hour <- data %>% 
    group_by(Time_hh) %>%
    summarise(mean_hourly_enmo = mean(mean_enmo, na.rm = TRUE))
  
  merged_data <- data %>% 
    left_join(mean_by_hour, by = "Time_hh")
  
  IS <- cor(merged_data$mean_enmo, merged_data$mean_hourly_enmo, use = "complete.obs")^2
  
  # Intradaily Variability (IV): Measures hour-to-hour variability
  sum_diff_squared <- sum((diff(data$mean_enmo))^2, na.rm = TRUE)
  sum_deviation_squared <- sum((data$mean_enmo - x_bar)^2, na.rm = TRUE)
  IV <- (n * sum_diff_squared) / ((n - 1) * sum_deviation_squared)
  
  return(data.frame(IS = IS, IV = IV))
}

# Apply this function by 'ID' and 'phase'
ISIV_results <- per_hour_data %>%
  group_by(ID, phase,Allocation) %>%
  arrange(DateTime) %>%
  summarise(IS_IV = list(calculate_IS_IV(cur_data()))) %>%
  unnest_wider(IS_IV) %>% 
  left_join(per_hour_data %>% 
              group_by(ID, phase,Allocation) %>% 
              summarise_at(vars(mean_enmo:time_M10_mu),~mean(.x,na.rm = T)))
ISIV_results$Allocation[ISIV_results$Allocation == "A"] <- "control"
ISIV_results$Allocation[ISIV_results$Allocation == "B"] <- "lithium"
```


```{r}

summary(l1<-lmer(IS ~ Allocation * phase + posLog + pos_vmu + (1|ID),ISIV_results))
summary(lmer(IS ~ Allocation * phase + movement_M10_vmu + posLog + pos_vmu + (1|ID),ISIV_results))

ee1 <- as.data.frame(Effect(c("phase", "Allocation"),l1))

stat.test <- as.data.frame(round(summary(l1)$coefficients,3))[c(6),]%>%
  rename(p_val = `Pr(>|t|)`)

stat.test$group1 <- c("post")
stat.test$group2 <- c("post")

stat.test <- left_join(stat.test,ee1[ee1$phase != "pre" & ee1$Allocation == "control",]%>%
  rename(group1 = phase))%>%
  mutate(y.position = ee1$upper[1])%>%
  mutate(p_sig = if_else(p_val < 0.001,"***", if_else(p_val < 0.01, "**", if_else(p_val < 0.05, "*", "ns")) ))

ggplot(ee1, aes(x = phase, y = fit, color = Allocation))+
  scale_color_manual(values=orangeNavyPalette)+
  geom_errorbar(aes(ymin = lower,ymax=upper),width=0.1,color = "black")+
    geom_point(size = 3)+
  geom_line(aes(group = Allocation), linewidth = 1)+
  theme(panel.grid.major.y = element_line(color = "black",size = 0.2),
        panel.grid.minor.y = element_blank(),
         panel.grid.major.x = element_blank())+
  labs(title = "",y="positive mood level")+ 
  stat_pvalue_manual(stat.test, label = "p_sig",vjust = -1)+
  scale_x_discrete(labels = c("run-in","post-randomization"))+
  ylim(0,1)

summary(l2<-lmer(IV ~ Allocation * phase + posLog + pos_vmu + (1|ID),ISIV_results))

ee2 <- as.data.frame(Effect(c("phase", "Allocation"),l2))

stat.test <- as.data.frame(round(summary(l2)$coefficients,3))[9:12,]%>%
  rename(p_val = `Pr(>|t|)`)
x
stat.test$group1 <- c("post")
stat.test$group2 <- c("post")

stat.test <- left_join(stat.test,ee2[ee2$phase != "pre" & ee2$Allocation == "control",]%>%
  rename(group1 = phase))%>%
  mutate(y.position = ee2$upper[1])%>%
  mutate(p_sig = if_else(p_val < 0.001,"***", if_else(p_val < 0.01, "**", if_else(p_val < 0.05, "*", "ns")) ))

ggplot(ee2, aes(x = phase, y = fit, color = Allocation))+
  scale_color_manual(values=orangeNavyPalette)+
  geom_errorbar(aes(ymin = lower,ymax=upper),width=0.1,color = "black")+
    geom_point(size = 3)+
  theme(panel.grid.major.y = element_line(color = "blackx",size = 0.2),
        panel.grid.minor.y = element_blank(),
         panel.grid.major.x = element_blank(),
        axis.text.x = element_text(angle=45))+
  labs(title = "",y="positive mood level")+ 
  stat_pvalue_manual(stat.test, label = "p_sig",vjust = -1)+
  scale_x_discrete(labels = c("run-in","post-randomization"))+
  ylim(0,1.5)
```


# show example time series of high vs. low vmu participants
```{r}
ranked_vmu<-df_hlm %>% 
  filter(phase != "pre",!is.na(movement_M10_vmu)) %>% 
  group_by(ID) %>% 
  summarise(mean_M10_vmu = mean(movement_M10_vmu,na.rm = T),
            mean_M10_s = mean(movement_M10_s,na.rm = T),
            valid_days = max(row_number())) %>% 
  arrange(mean_M10_vmu,desc(mean_M10_s))

min_id = c("OL0039","OL0369") #ranked_vmu$ID[1:4]
max_id = c("OL0191","OL0136") #ranked_vmu$ID[(nrow(ranked_vmu)-3):nrow(ranked_vmu)]

p1<-ggplot(df_hlm %>% 
  filter(phase != "pre")%>% 
         filter(ID %in% c(max_id,min_id)) %>% 
         mutate(group = ifelse(ID %in% max_id, "high_volatility","low_volatility")), 
       aes(x = day, y = movement_M10_mean))+
  geom_line(aes(group = ID, color = ID),linewidth = 1)+
  scale_color_brewer(palette = "Dark2")+
  facet_wrap(~group)+
  scale_x_continuous(breaks = c(1,7,14,21,28))+
  theme(legend.position = "none")+
  labs(y = "daily M10 level",
       x = "days post-randomization")


rankeds<-df_hlm %>% 
  filter(phase != "pre",!is.na(movement_M10_s)) %>% 
  group_by(ID)  %>% 
  summarise(mean_M10_vmu = mean(movement_M10_vmu,na.rm = T),
            mean_M10_s = mean(movement_M10_s,na.rm = T),
            valid_days = max(row_number())) %>% 
  arrange(mean_M10_s,desc(mean_M10_vmu))

min_id = c("OL0191","OL0369") #rankeds$ID[1:4]
max_id = c("OL0002","OL0025")#rankeds$ID[(nrow(rankeds)-3):nrow(rankeds)]

p2<-ggplot(df_hlm %>% 
  filter(phase != "pre")%>% 
         filter(ID %in% c(max_id,min_id)) %>% 
         mutate(group = ifelse(ID %in% max_id, "high_noise","low_noise")), 
       aes(x = day, y = movement_M10_mean))+
  geom_line(aes(group = ID, color = ID),linewidth = 1)+
  scale_color_brewer(palette = "Set1")+
  facet_wrap(~group)+
  scale_x_continuous(breaks = c(1,7,14,21,28))+
  theme(legend.position = "none")+
  labs(y = "daily M10 level",
       x = "days post-randomization")

p1+p2
ggsave("../figs/R2_example.png",width = 7,height=3,dpi = 300)
```

# analyze week-of-day and seasonal effect
## first, does these factors influence M10, L5 and their onset time?
```{r}
summary(l1<-lmer(movement_M10_mean ~ Season + weekday_weekend+ (1|ID),df_hlm))
summary(l2<-lmer(movement_L5_mean ~ Season + weekday_weekend+ (1|ID),df_hlm))
summary(l3<-lmer(time_M10_mean ~ Season + weekday_weekend + (1|ID),df_hlm))
summary(l4<-lmer(time_L5_mean ~ Season + weekday_weekend+ (1|ID),df_hlm))
summary(lmer(posLog ~ Season + weekday_weekend + (1|ID),df_hlm))
summary(lmer(negLog ~ Season + weekday_weekend + (1|ID),df_hlm))
summary(lmer(posLog ~ Datey + (1|ID),df_hlm))

plot_model(l4, type = "pred", terms = "weekday_weekend")

plot_model(l1, type = "pred", terms = "Datey")
plot_model(l2, type = "pred", terms = "Datey")
plot_model(l3, type = "pred", terms = "Datey")
plot_model(l4, type = "pred", terms = "Datey")


summary(l1<-lmer(movement_M10_vmu ~ Season + weekday_weekend+ (1|ID),df_hlm))
summary(l2<-lmer(movement_M10_s ~ Season + weekday_weekend+ (1|ID),df_hlm))
summary(l3<-lmer(time_M10_vmu ~ Season + weekday_weekend + (1|ID),df_hlm))
summary(l4<-lmer(time_M10_s ~ Season + weekday_weekend+ (1|ID),df_hlm))
```

# separate models for everything
```{r}
summary(lmer(movement_M10_mean ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season + movement_L5_mean + (1|ID),data = df_hlm))
summary(lmer(movement_L5_mean ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season +movement_M10_mean+ (1|ID),data = df_hlm))
summary(lmer(time_M10_mean ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season +time_L5_mean+ (1|ID),data = df_hlm))
summary(lmer(time_L5_mean ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season  +time_L5_mean+ (1|ID),data = df_hlm))

summary(lmer(movement_M10_vmu ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season +movement_M10_s+ (1|ID),data = df_hlm))
summary(lmer(movement_M10_s ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season +movement_M10_vmu+ (1|ID),data = df_hlm))
summary(lmer(movement_L5_vmu ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season +movement_L5_vmu+ (1|ID),data = df_hlm))
summary(lmer(movement_L5_s ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season + movement_L5_vmu+(1|ID),data = df_hlm))

summary(lmer(time_M10_vmu ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season+time_M10_s + (1|ID),data = df_hlm))
summary(lmer(time_M10_s ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season +time_M10_vmu+ (1|ID),data = df_hlm))
summary(lmer(time_L5_vmu ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season + time_L5_s+(1|ID),data = df_hlm))
summary(lmer(time_L5_s ~ Allocation * phase + posLog + pos_vmu + Age + Gender + Season + time_L5_vmu+(1|ID),data = df_hlm))
```

# fitting model to only post weeks
### raw value
```{r}
model_formula_mean <- val ~ Allocation * movement_type * phase + posLog + pos_vmu  + Age + Gender + Season +  (movement_type|ID)

df_hlm_lmer_movement_mean2 <- df_hlm%>%
  filter(phase != "pre") %>% 
  select(ID,Allocation,phase,day,movement_L5_mean,movement_M10_mean,Age,Gender,posLog, negLog, pos_vmu,neg_vmu,Season,
         Dateseason,weekday_weekend)%>%
  pivot_longer(c(movement_L5_mean,movement_M10_mean),names_pattern =  "movement_(.*)_mean",names_to = c("movement_type"),values_to = "val")

df_hlm_lmer_movement_mean2$movement_type <- factor(df_hlm_lmer_movement_mean$movement_type)
df_hlm_lmer_movement_mean2$movement_type <- relevel(df_hlm_lmer_movement_mean2$movement_type, ref = "M10")

df_hlm_lmer_movement_mean2$Allocation <- factor(df_hlm_lmer_movement_mean2$Allocation, levels = c("control","lithium"))
summary(lmer(model_formula_mean,data = df_hlm_lmer_movement_mean2))
```

### variability
```{r include=TRUE}
model_formula <- val ~ Allocation * var_type * movement_type * phase + posLog + pos_vmu + Age + Gender + Season + (var_type * movement_type| ID)

df_hlm_lmer_movement_variability2 <- df_hlm%>%
  filter(phase != "pre") %>% 
  select(ID,Season,Allocation,day,phase,movement_L5_s,movement_L5_vmu, movement_M10_s,movement_M10_vmu,Age,Gender,posLog, negLog, pos_vmu,neg_vmu,
         Dateseason,weekday_weekend)%>%
  pivot_longer(c(movement_L5_s,movement_L5_vmu, movement_M10_s,movement_M10_vmu),names_pattern =  "movement_(.*)_(.*)",names_to = c("movement_type","var_type"),values_to = "val")%>%
  mutate(var_type = if_else(var_type == "vmu","volatility","noise"))

df_hlm_lmer_movement_variability2$var_type <- factor(df_hlm_lmer_movement_variability2$var_type)
df_hlm_lmer_movement_variability2$var_type <- relevel(df_hlm_lmer_movement_variability2$var_type, ref = "volatility")
df_hlm_lmer_movement_variability2$movement_type <- factor(df_hlm_lmer_movement_variability2$movement_type)
df_hlm_lmer_movement_variability2$movement_type <- relevel(df_hlm_lmer_movement_variability2$movement_type, ref = "M10")
df_hlm_lmer_movement_variability2$Allocation <- factor(df_hlm_lmer_movement_variability2$Allocation, levels = c("control","lithium"))

summary(lmer(model_formula,data = df_hlm_lmer_movement_variability2))
```